Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-16 doc/GMP2015/s01_introduction.tex

>>>>

\begin{figure*}\centering
\begin{subfigure}{.31\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Axopodium_Mikrotubuli}
  \caption{Cross section of a Heliozoa's psuedopod, formed by a spiral structure of microtubules.}
  % https://de.wikipedia.org/wiki/Mikrotubulus#mediaviewer/File:Axopodium_Mikrotubuli.jpg
  \label{fig:microtubule}
\end{subfigure}\hfill
\begin{subfigure}{.31\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Transverse_Section_Of_Bone}
  \caption{Cross section of an osteon (the fundamental unit of compact bone) exhibiting its hierarchical structure.}
  % https://en.wikipedia.org/wiki/Osteon#mediaviewer/File:Transverse_Section_Of_Bone.png
  \label{fig:osteon}
\end{subfigure}\hfill
\begin{subfigure}{.31\linewidth}\centering
  \includegraphics[width=\linewidth]{img/Rothemund-DNA-SierpinskiGasket}
  \caption{A DNA array exhibiting the Sierpinski triangle.}
  % https://en.wikipedia.org/wiki/DNA_nanotechnology#mediaviewer/File:Rothemund-DNA-SierpinskiGasket.jpg
  \label{fig:sierpinski}
\end{subfigure}
\caption{}
\end{figure*}
